Prizm Silver Rookie Cards

### 2024-04-25 paper/paper.qmd
fix cross refference issue

After taking a closer look at trends from both predicted and past data, an interesting point came up mind. When observing turning points of the price, they all seems to be the start and end of a season. Price increasing trends tends to happen at the start of each season, and then become more and more unpredictable throughout the season. This brings attention to the timing of the season and the price may be quite related and even more than the player statistics. Because despite implementing an increasing performance for each of the player statistics to run the model on, there are no clear signs of increasing price overall. The thing that stood out the most is the price increase at the start of every season in October. This could suggest that the initial hype of a new season could be contrbuting to the increase of the card price.

@@

Future steps would include categorizing each player based on their positions and giving weight to the statistics that would have a better indication of their performance. For example, giving more weight to the average number of blocks per game for defensive players. Upon taking a look at @fig-4, @fig-5, and @fig-6, the fit of the data are not very good. Another step would be the incorporation of other models to find better fits, because of the complex relationship between the price and the player statistics, a more sophisticated model may be needed. I think also using an average of all the player's statistics and price data and compare them to individual model would also be something beneficial, exploring the overall relationship rather than one at a time. Overall, this analysis gives insgitht to how complex the relationship is and that a lot more work would be required to be done.

@@

## Model Check

>>>>

After taking a closer look at trends from both predicted and past data, an interesting point came up mind. When observing turning points of the price, they all seems to be the start and end of a season. Price increasing trends tends to happen at the start of each season, and then become more and more unpredictable throughout the season. This brings attention to the timing of the season and the price may be quite related and even more than the player statistics. Because despite implementing an increasing performance for each of the player statistics to run the model on, there are no clear signs of increasing price overall. The thing that stood out the most is the price increase at the start of every season in October. This could suggest that the initial hype of a new season could be contributing to the increase of the card price.

@@

Future steps would include categorizing each player based on their positions and giving weight to the statistics that would have a better indication of their performance. For example, giving more weight to the average number of blocks per game for defensive players. Upon taking a look at @sec-modelcheck, the fit of the data are not very good. Another step would be the incorporation of other models to find better fits, because of the complex relationship between the price and the player statistics, a more sophisticated model may be needed. I think also using an average of all the player's statistics and price data and compare them to individual model would also be something beneficial, exploring the overall relationship rather than one at a time. Overall, this analysis gives insgitht to how complex the relationship is and that a lot more work would be required to be done.

@@

## Model Check {#sec-modelcheck}
